---
title: Javier Elío
date: "`r format(Sys.time(), '%B %Y')`"
bibliography: CV_Elio.bib
csl: vancouver.csl 
output:
  pdf_document:
    df_print: kable
    latex_engine: xelatex
subparagraph: yes
header-includes:
  - \usepackage{colortbl}
  - \arrayrulecolor{white}
  - \usepackage{fancyhdr}
  - \definecolor{Col_title}{HTML}{DC3522}
  - \definecolor{Col_sub_title}{HTML}{00A388}
  - \geometry{left = 1.9cm, top = 1.95cm, right = 1.9cm, bottom = 1.9cm, footskip = .5cm}
  - \usepackage{tcolorbox}
  - \definecolor{light-yellow}{rgb}{1, 0.95, 0.7}
  - \newtcolorbox{mybox}{colback = light-yellow, boxrule = 0pt, boxsep = 0pt}
  - \newcommand{\colbox}[1]{\begin{mybox} {#1} \end{mybox}}
  - \definecolor{colorbox}{rgb}{0.9, 0.9, 0.98}
  - \usepackage{titlesec}
  - \titlespacing{\section}{0pt}{13pt}{5pt}
  - \titlespacing{\subsection}{0pt}{13pt}{5pt}
  - \titlespacing{\subsubsection}{0pt}{13pt}{5pt}
  - \let\oldrule=\rule
  - \renewcommand{\rule}[1]{\oldrule{\linewidth}}
  - \titleformat{\section}{\vspace{-5pt}\normalfont\Large\bfseries}{\thesection}{1em}{}[{\vspace{-0.3ex} \titlerule[0.5pt]}]
  - \pagestyle{fancy}
  - \fancyhf{}
  - \pagenumbering{roman}
  - \renewcommand{\headrulewidth}{0pt}
  - \rhead{\thedate}
  - \lhead{CV Javier El\'{i}o}
  - \rfoot{Page \thepage}
urlcolor: blue
fontsize: 11pt
linestretch: 1
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
library(tidyverse)
library(RefManageR)
library(knitr)
library(kableExtra)
source("CV_Table.R")

```

```{r bibfiles}
# Read any bib files
pubs <- ReadBib("CV_Elio.bib", check = FALSE)

```
  
```{r GS}
My_GS <- scholar::get_profile("NF5SYm8AAAAJ&hl")
```

\renewcommand{\arraystretch}{1.5}
# \textcolor{Col_title}{Per}sonal information
```{r ,  results = 'asis'}
col1 <- "\\href{https://twitter.com/Elio_Javi/}{@Elio\\_Javi}"
col2 <- "\\href{https://www.researchgate.net/profile/Javier_Elio/}{Javier\\_Elio}"
col3 <- "\\href{https://github.com/javiereliomedina/}{javiereliomedina}"
col4 <- "\\href{https://www.linkedin.com/in/javiereliomedina/}{javiereliomedina}"

test <- data.frame(V1 = c("Address", "Phone", "email", " "),
                   V2 = c("Haugesund (Norway)","(+47) 4125 91 17", "javiereliomedina@gmail.com", " "),
                   V3 = c("Twitter", "ResearchGate", "Github", "Linkedin"),
                   V4 = c(col1, col2, col3, col4)
                   )

knitr::kable(test,format = 'latex',
                 col.names = NULL,
                 escape = F,
                 linesep = "") %>%
    kableExtra::kable_styling(full_width = F) %>%
    kableExtra::column_spec(1, bold = TRUE, width = "7em", background = "colorbox") %>%
    kableExtra::column_spec(2, width = "12em", background = "colorbox") %>%
    kableExtra::column_spec(3, bold = TRUE, width = "7em",
                            background = "colorbox", border_left = TRUE) %>%
    kableExtra::column_spec(4, width = "12em",
                            background = "colorbox") 
```
\renewcommand{\arraystretch}{1}
\vspace{-5pt}
# \textcolor{Col_title}{Car}eer Summary
\vspace{5pt}
I am a Mining Engineer, with an MSc in Environmental Research, Modelling and Risk Assessment, and a PhD in Environmental Sciences. For the last years, I have been working on radon mapping at the Geology Department at Trinity College Dublin, although I have also experience in monitoring geological storage of $CO_{2}$, and in geochemical characterization of contaminated sites. 

My research interests are: 

+	Environmental risk assessment
+	Radon mapping
+ Radon measurements in air, soil, and water
+	Natural radioactivity, Natural Occurrence Radioactive Materials (NORM)
+	Statistics, spatial data analysis, and geostatistics (R language)
+ Geographic information systems 

# \textcolor{Col_title}{Edu}cation
```{r Education,  results = 'asis'}
readxl::read_excel("CV_Elio.xlsx", sheet = "Education") %>%
  mutate(Degree = str_c("\\textbf{", Degree, "}")) %>%
  mutate(Details = str_c(Degree, Institution, Where, sep = ", ")) %>%
  select(Year, Details) %>%
  CV_Table()  
```

# \textcolor{Col_title}{Exp}erience
```{r experience, results = 'asis'}
readxl::read_excel("CV_Elio.xlsx", sheet = "Experience") %>%
  mutate(Role = str_c("\\textbf{", Role, "}")) %>%
  mutate(Details = str_c(Role, Company, Where, sep = ", ")) %>%
  select(Year, Details) %>%
  CV_Table() 
```

# \textcolor{Col_title}{Pro}fessional memberships
```{r memberships, results = 'asis'}
readxl::read_excel("CV_Elio.xlsx", sheet = "Memberships") %>%
  mutate(Role = str_c("\\textbf{", Role, "}")) %>%
  mutate(Details = str_c(Role, Institution, Where, sep = ", ")) %>%
  select(Year, Details) %>%
  CV_Table() 
```

# \textcolor{Col_title}{Pro}fessional Services
```{r Services, results = 'asis'} 
tribble(
  ~Year, ~Institution, ~Role,
  "2018/19", "\\textbf{International Atomic Energy Agency (IAEA)}", "Expert missions on Radon Mapping and National Radon Action Plans: Peru (August 2018), Cyprus (October 2018), Lithuania (July 2019).",
  
  "2018", "\\textbf{European Commission, Joint Research Centre (JRC)}", "Invite as an expert to the meeting -Working Group Meeting on Indoor Radon Dose- (May 2018, Ispra, Italy)."
  ) %>% 
  mutate(Details = str_c(Institution, Role, sep = ", ")) %>%
  select(Year, Details) %>%
  CV_Table()
  
```

# \textcolor{Col_title}{Fun}ding projects

## *\textcolor{Col_sub_title}{Awa}rded*
```{r Awarded, results = 'asis'}
readxl::read_excel("CV_Elio.xlsx", sheet = "Projects") %>%
  filter(Status == "Awarded") %>%
  mutate(Source = str_c("\\textbf{", Source, "}"),
         Details = str_c(Source, Details, Host, Where, sep = ", ")) %>%
  select(Year, Details) %>%
  CV_Table()
``` 

## *\textcolor{Col_sub_title}{Und}er assessment*
```{r Assessment, results = 'asis'}
readxl::read_excel("CV_Elio.xlsx", sheet = "Projects") %>% 
  filter(Status == "Under assessment") %>%
  mutate(Source = str_c("\\textbf{", Source, "}"),
         Details = str_c(Source, Details, Host, Where, sep = ", ")) %>%
  select(Year, Details) %>%
  CV_Table()
```

## *\textcolor{Col_sub_title}{Rej}ected*
```{r Rejected, results = 'asis'}
readxl::read_excel("CV_Elio.xlsx", sheet = "Projects") %>% 
  filter(Status == "Rejected") %>%
  mutate(Source = str_c("\\textbf{", Source, "}"),
         Details = str_c(Source, Details, Host, Where, sep = ", ")) %>%
  select(Year, Details) %>%
  CV_Table()
```

# \textcolor{Col_title}{Gra}nts
```{r grants, results = 'asis'}
readxl::read_excel("CV_Elio.xlsx", sheet = "Grants") %>%
  mutate(Source = str_c("\\textbf{", Source, "}"),
         Details = str_c(Source, Institution, Details, Where, sep = ", ")) %>%
  select(Year, Details) %>%
  CV_Table()
```

# \textcolor{Col_title}{Hon}ours and Awards
```{r awards, results = 'asis'}
readxl::read_excel("CV_Elio.xlsx", sheet = "Awards") %>%
  mutate(Name = str_c("\\textbf{", Name, "}"),
         Details = str_c(Name, Details, Where, sep = ", ")) %>%
  select(Year, Details) %>%
  CV_Table()
```

# \textcolor{Col_title}{Res}earch Stays
```{r stays, results = 'asis'} 
tribble(
  ~Year, ~University, ~Details, ~Where,
  2013, "University of Florence", "invited by Prof. Orlando Vaselli (duration 3 months)", "Florence (Italy)") %>%
  mutate(University = str_c("\\textbf{", University, "}"),
         Details = str_c(University, Details, Where, sep = ", ")) %>%
  select(Year, Details) %>%
  CV_Table()
```

# \textcolor{Col_title}{Tea}ching Experience

## *\textcolor{Col_sub_title}{PhD} Examiner*
```{r PhD Examiner, results = 'asis'}
readxl::read_excel("CV_Elio.xlsx", sheet = "Teaching") %>% 
  filter(Type == "PhD Examiner") %>%
  mutate(Role = str_c("\\textbf{", Role, "}"),
         Details = str_c(Role, Details, Where, sep = ", ")) %>%
  select(Year, Details) %>%
  CV_Table()
``` 

## *\textcolor{Col_sub_title}{Sup}ervision*
```{r Supervision, results = 'asis'}
readxl::read_excel("CV_Elio.xlsx", sheet = "Teaching") %>% 
  filter(Type == "Supervision") %>%
  mutate(Role = str_c("\\textbf{", Role, "}"),
         Details = str_c(Role, Details, Where, sep = ", ")) %>%
  select(Year, Details) %>%
  CV_Table()
```

## *\textcolor{Col_sub_title}{Lec}tures/Seminars*
```{r Lectures, results = 'asis'}
readxl::read_excel("CV_Elio.xlsx", sheet = "Teaching") %>% 
  filter(Type == "Lectures") %>%
  mutate(Role = str_c("\\textbf{", Role, "}"),
         Details = str_c(Role, Details, Where, sep = ", ")) %>%
  select(Year, Details) %>%
  CV_Table()
```

# \textcolor{Col_title}{Pub}lications
\vspace{8pt}
I have published **`r length(pubs)`** peer-reviewed journal articles, chapters or books on Environmental Science topics. I have also presented my research at 3 invited talks, and in several national and international conferences including AGU, EGU, EAGE, IGC and Goldschmidt. My metrics in **Google Scholar** are:

\vspace{8pt}
+ Total citations: `r My_GS$total_cites`
+ h-index: `r My_GS$h_index`
+ i10-index: `r My_GS$i10_index`
\vspace{8pt}

---
nocite: | 
  @Elio2019b, @Elio2019a, @Nisi2019,
  @Barrio-Parra2018, @DeMiguel2018, @Elio2018,
  @Elio2017,
  @Elio2016b, @Elio2016,
  @Elio2015b, @Elio2015a,
  @Nisi2014, @Ortega2014, @Llamas2014,
  @Elio2013, @Nisi2013,
  @Elio2012
...
