---
name: Javier 
surname: Elío
date: "`r format(Sys.time(), '%B, %Y')`"
position: Researcher | Environemntal sciences | Data Sciences
address: Haugesund (Norway)
phone: +47 4125 91 17
email: javiereliomedina@gmail.com
website: researchgate.net/profile/Javier_Elio
github: javiereliomedina
linkedin: javiereliomedina
twitter: Elio_Javi
output: vitae::awesomecv
header-includes:
  - \usepackage{colortbl}
  - \arrayrulecolor{white}
  - \photo[circle, noedge, left]{photo.png}
  - \definecolor{darktext}{HTML}{414141}
  - \definecolor{blue}{rgb}{0.0, 0.0, 1.0}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
library(tidyverse)
library(RefManageR)
library(knitr)
library(kableExtra)
library(vitae)
library(bib2df)
library(rorcid)
library(janitor)
library(rcrossref)
  
source("CV_Table.R")
source("Escape_Latex_Specials.R")
```

```{r ORCID_Works}
# Get ORCID API Key and save it in Renviron  
# orcid_auth()               # API key (without Bearer)
# usethis::edit_r_environ()  # Open up the Renviron file
# save the key as: ORCID_TOKEN="yourkey"
# Restart the R session
# We can see the key with Sys.getenv("ORCID_TOKEN")

# When possible I choose "Scopus - Elsevier" as the "Preferred Source" and delate the rest
# that way all articles will have the same format

# Get works
  id <- "0000-0003-0624-2345"
  out <- works(orcid_id(id)) 
  wks <- orcid_works(id, out$`put-code`)
  
# Extract publication information 
  Authors <- vector()
  for (i in seq_along(wks[[id]]$works$work.contributors.contributor)) {
    Authors[[i]] <-str_c(wks[[id]]$works$work.contributors.contributor[[i]]$`credit-name.value`, collapse = "; ")
  }
  
  DOI <- vector()
  for (i in seq_along(wks[[id]]$works$work.contributors.contributor)) {
    DOI[[i]] <- wks[[id]]$works$`work.external-ids.external-id`[[i]]$`external-id-value`[1]
  }
  
  pubs <- tibble(Type = wks[[id]]$works$work.type,
                 Year = wks[[id]]$works$`work.publication-date.year.value`,
                 Authors = Authors,
                 Title = wks[[id]]$works$work.title.title.value,
                 Journal = wks[[id]]$works$`work.journal-title.value`,
                 DOI = DOI) %>%
    distinct(DOI, .keep_all = TRUE) %>% 
    mutate(DOI = replace(DOI, DOI == "2-s2.0-84899952872", "10.30955/gnj.001242"), 
           DOI = replace(DOI, DOI == "2-s2.0-84899963838", "10.30955/gnj.001241"),
           Authors = str_replace_all(Authors, "Elio", "Elío"),
           Authors = str_replace_all(Authors, "de Elío", "Elío")) %>%
    filter(Type == "journal-article" | Type == "book")      
  
# Add volume and pages 
  VP <- rcrossref::cr_cn(dois = pubs$DOI, format = "bibtex")
  
  pubs <- pubs %>%
    mutate(Volume = str_match(VP, "volume = \\{(.*[0-9])")[,2],
           Pages = str_match(VP, "pages = \\{(.*[0-9])")[,2]) 
# Remove latex symbols for knit
  pubs <- pubs %>%
    mutate(Authors = Escape_Latex_Specials(Authors),
           Title   = Escape_Latex_Specials(Title),
           Journal = Escape_Latex_Specials(Journal),
           DOI     = Escape_Latex_Specials(DOI))
```
 
\vspace{-0.1cm}
\footnotesize 
\rightline{\textcolor{darktext}{"Expert on environmental research, statistics, spatial data analysis, and modelling."}} 
\normalsize

# Education
\vspace{-0.20cm}
```{r Education,  results = 'asis'}
 edu_ORCID <- orcid_educations(id)
  
  edu <- matrix(NA, length(edu_ORCID[[id]]$`affiliation-group`$summaries), 6)
  for (i in seq_along(edu_ORCID[[id]]$`affiliation-group`$summaries)) {
   edu[i, 1] <- edu_ORCID[[id]][[2]]$summaries[[i]]$`education-summary.start-date.year.value`
   edu[i, 2] <- edu_ORCID[[id]][[2]]$summaries[[i]]$`education-summary.end-date.year.value`
   edu[i, 3] <- edu_ORCID[[id]][[2]]$summaries[[i]]$`education-summary.role-title`
   edu[i, 4] <- edu_ORCID[[id]][[2]]$summaries[[i]]$`education-summary.organization.name`
   edu[i, 5] <- edu_ORCID[[id]][[2]]$summaries[[i]]$`education-summary.organization.address.city`
   edu[i, 6] <- edu_ORCID[[id]][[2]]$summaries[[i]]$`education-summary.organization.address.country`
  }
  
  edu <- as_tibble(edu) %>%
    rename(Year_Start = V1,
           Year_End = V2,
           Title = V3,
           Uni = V4,
           City = V5,
           Country = V6) 
  
  edu %>% 
    mutate(Year_End = str_sub(Year_End, -2), 
           Year = str_c(Year_Start, Year_End, sep = "-"),
           Title = str_c("\\textbf{", Title, "}"), 
           Details = str_c(Title, Uni, City, Country, sep = ", "),
           Details = str_c(Details, ". ")) %>%
    select(Year, Details) %>%
    CV_Table()
```
\vspace{-0.75cm}
# Experience
\vspace{-0.20cm}
```{r experience, results = 'asis'}
  exp_ORCID <- orcid_employments(id)
  
  exp <- matrix(NA, length(exp_ORCID$`0000-0003-0624-2345`$`affiliation-group`$summaries), 7)
  for (i in seq_along(exp_ORCID$`0000-0003-0624-2345`$`affiliation-group`$summaries)) {
    exp[i, 1] <- exp_ORCID[[id]][[2]]$summaries[[i]]$`employment-summary.start-date.year.value`
    exp[i, 2] <- exp_ORCID[[id]][[2]]$summaries[[i]]$`employment-summary.end-date.year.value`
    exp[i, 3] <- exp_ORCID[[id]][[2]]$summaries[[i]]$`employment-summary.role-title`
    exp[i, 4] <- exp_ORCID[[id]][[2]]$summaries[[i]]$`employment-summary.organization.name`
    exp[i, 5] <- exp_ORCID[[id]][[2]]$summaries[[i]]$`employment-summary.department-name`
    exp[i, 6] <- exp_ORCID[[id]][[2]]$summaries[[i]]$`employment-summary.organization.address.city`
    exp[i, 7] <- exp_ORCID[[id]][[2]]$summaries[[i]]$`employment-summary.organization.address.country`
  }
  
  exp <- as_tibble(exp) %>%
    rename(Year_Start = V1,
           Year_End = V2,
           Role = V3,
           Company = V4,
           Depart = V5,
           City = V6, 
           Country = V7) 
  
  exp %>% 
    mutate(Year_End = str_sub(Year_End, -2), 
           Year = str_c(Year_Start, Year_End, sep = "-"),
           Role = str_c("\\textbf{", Role, "}"), 
           Details = str_c(Role, Company, Depart, City, Country, sep = ", "),
           Details = str_c(Details, ". ")) %>%
    select(Year, Details) %>%
    arrange(desc(Year)) %>%
    CV_Table()
```
\vspace{-0.7cm}
# Professional Services
\vspace{-0.20cm}
```{r Services, results = 'asis'} 
tribble(
  ~Year, ~Institution, ~Role,
  "2018/19", "\\textbf{International Atomic Energy Agency (IAEA)}", "Expert missions on Radon Mapping and National Radon Action Plans: Peru (August 2018), Cyprus (October 2018), Lithuania (July 2019)",
  
  "2018", "\\textbf{European Commission, Joint Research Centre (JRC)}", "Invite as an expert to the meeting -Working Group Meeting on Indoor Radon Dose- (May 2018, Ispra, Italy)"
  ) %>% 
  mutate(Details = str_c(Institution, Role, sep = ", ")) %>%
  select(Year, Details) %>%
  CV_Table()
```
\vspace{-0.7cm}
# Professional memberships
\vspace{-0.20cm}
```{r memberships, results = 'asis'}
  mem_ORCID <- orcid_memberships(id)
  
  mem <- matrix(NA, length(mem_ORCID[[id]][[2]]$summaries), 7)
  for (i in seq_along(mem_ORCID[[id]][[2]]$summaries)) {
    mem[i, 1] <- mem_ORCID[[id]][[2]]$summaries[[i]]$`membership-summary.start-date.year.value`
    mem[i, 2] <- mem_ORCID[[id]][[2]]$summaries[[i]]$`membership-summary.end-date`
    mem[i, 3] <- mem_ORCID[[id]][[2]]$summaries[[i]]$`membership-summary.role-title`
    mem[i, 4] <- mem_ORCID[[id]][[2]]$summaries[[i]]$`membership-summary.organization.name`
    mem[i, 5] <- mem_ORCID[[id]][[2]]$summaries[[i]]$`membership-summary.department-name`
    mem[i, 6] <- mem_ORCID[[id]][[2]]$summaries[[i]]$`membership-summary.organization.address.city`
    mem[i, 7] <- mem_ORCID[[id]][[2]]$summaries[[i]]$`membership-summary.organization.address.country`
    }
  
  mem <- as_tibble(mem) %>%
    rename(Year_Start = V1,
           Year_End = V2,
           Role = V3,
           Company = V4,
           Depart = V5,
           City = V6, 
           Country = V7) 
  
  mem %>% 
    mutate(Year_End = str_replace_na(Year_End),
           Depart = str_replace_na(Depart),
           Year = str_c(Year_Start, Year_End, sep = "-"),
           Year = str_replace(Year, "NA", ""),
           Company = str_c("\\textbf{", Company, "}"), 
           Details = str_c(Company, Depart, City, Country, sep = ", "),
           Details = str_replace(Details, "NA,", ""),
           Details = str_c(Details, ". ")) %>%
    select(Year, Details) %>%
    arrange(desc(Year)) %>%
    CV_Table() 
```
\vspace{-0.7cm}
# Honours and Awards
\vspace{-0.20cm}
```{r funding, results = 'asis'}
 fund_ORCID <- orcid_fundings(id)
  
  fund <- matrix(NA, length(fund_ORCID[[id]][[2]]$`funding-summary`), 7)
  for (i in seq_along(fund_ORCID[[id]][[2]]$`funding-summary`)) {
    fund[i, 1] <- fund_ORCID[[id]][[2]]$`funding-summary`[[i]]$type
    fund[i, 2] <- fund_ORCID[[id]][[2]]$`funding-summary`[[i]]$`start-date.year.value`
    fund[i, 3] <- fund_ORCID[[id]][[2]]$`funding-summary`[[i]]$`end-date.year.value`
    fund[i, 4] <- fund_ORCID[[id]][[2]]$`funding-summary`[[i]]$title.title.value
    fund[i, 5] <- fund_ORCID[[id]][[2]]$`funding-summary`[[i]]$organization.name
    fund[i, 6] <- fund_ORCID[[id]][[2]]$`funding-summary`[[i]]$organization.address.city
    fund[i, 7] <- fund_ORCID[[id]][[2]]$`funding-summary`[[i]]$organization.address.country
  }
  
  fund <- as_tibble(fund) %>%
    rename(Type = V1,
           Year_Start = V2,
           Year_End = V3,
           Title = V4,
           Company = V5,
           City = V6, 
           Country = V7)
```
```{r awards, results = 'asis'}
 fund %>% 
    filter(Type == "award") %>%
    mutate(Year = Year_Start,
           Title = str_c("\\textbf{", Title, "}"), 
           Details = str_c(Title, Company, City, Country, sep = ", "),
           Details = str_replace(Details, "NA,", ""),
           Details = str_c(Details, ". ")) %>%
    select(Year, Details) %>%
    arrange(desc(Year)) %>%
    CV_Table()
```
\vspace{-0.75cm}
# Other skills
\vspace{-0.15cm}
+ I have published **`r length(pubs$Type)`** peer-reviewed journal articles, chapters or books on Environmental Science topics
+ Advanced R experience
+ Solid technical skills in Geographic Information System (R and ArcGIS) 
+ Language skills: Spanish (mother tongue); English (fluent); Norwegian (basic)
