---
name: Javier 
surname: Elío
date: "`r format(Sys.time(), '%B, %Y')`"
position: Researcher | Environemntal sciences | Data Sciences
address: Haugesund (Norway)
phone: +47 4125 91 17
email: javiereliomedina@gmail.com
website: researchgate.net/profile/Javier_Elio
github: javiereliomedina
linkedin: javiereliomedina
twitter: Elio_Javi
output: vitae::awesomecv
header-includes:
  - \usepackage{colortbl}
  - \arrayrulecolor{white}
  - \photo[circle, noedge, left]{photo.png}
  - \definecolor{darktext}{HTML}{414141}
  - \definecolor{blue}{rgb}{0.0, 0.0, 1.0}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
library(tidyverse)
library(knitr)
library(kableExtra)
library(rorcid)
library(rcrossref)
  
source("CV_table.R")
source("Escape_latex_specials.R")
```

```{r ORCID_Works}
# Get ORCID API Key and save it in Renviron  
# orcid_auth()               # API key (without Bearer)
# usethis::edit_r_environ()  # Open up the Renviron file
# save the key as: ORCID_TOKEN="yourkey"
# Restart the R session
# We can see the key with Sys.getenv("ORCID_TOKEN")

# When possible I choose "Scopus - Elsevier" as the "Preferred Source" and delate the rest
# that way all articles will have the same format

# Get works
  id <- "0000-0003-0624-2345"
  out <- works(orcid_id(id)) 
  wks <- orcid_works(id, out$`put-code`)

# Alternative names and bold my surname in the pdf
  replace_my_name <- function(x) {
    x <- str_replace_all(x, "Elio", "Elío")
    x <- str_replace_all(x, "de Elío", "Elío")
    x <- str_replace_all(x, "Medina, J.E.", "Elío, J.")
    x <- str_replace_all(x, "Elío", "\\\\textbf{Elío}")
    }

# Bold text in the pdf
  bold_text <- function(x) {x <- str_c("\\textbf{", x, "}")}

# Extract publication information 
  Authors <- vector()
  for (i in seq_along(wks[[id]]$works$work.contributors.contributor)) {
    Authors[[i]] <-str_c(wks[[id]]$works$work.contributors.contributor[[i]]$`credit-name.value`, collapse = "; ")
  }
  
  DOI <- vector()
  for (i in seq_along(wks[[id]]$works$work.contributors.contributor)) {
    DOI[[i]] <- wks[[id]]$works$`work.external-ids.external-id`[[i]]$`external-id-value`[1]
  }
  
  pubs <- tibble(Type = wks[[id]]$works$work.type,
                 Year = wks[[id]]$works$`work.publication-date.year.value`,
                 Authors = Authors,
                 Title = wks[[id]]$works$work.title.title.value,
                 Journal = wks[[id]]$works$`work.journal-title.value`,
                 DOI = DOI) %>%
    distinct(DOI, .keep_all = TRUE) %>% 
    mutate(DOI = replace(DOI, DOI == "2-s2.0-84899952872", "10.30955/gnj.001242"), 
           DOI = replace(DOI, DOI == "2-s2.0-84899963838", "10.30955/gnj.001241"),
           Authors = replace_my_name(Authors)) %>%
    filter(Type == "journal-article" | Type == "book")      
  
# Add volume and pages 
  VP <- rcrossref::cr_cn(dois = pubs$DOI, format = "bibtex")
  
  pubs <- pubs %>%
    mutate(Volume = str_match(VP, "volume = \\{(.*[0-9])")[,2],
           Pages = str_match(VP, "pages = \\{(.*[0-9])")[,2]) 
# Remove latex symbols for knit
  pubs <- pubs %>%
    mutate(Authors = Escape_latex_specials(Authors),
           Title   = Escape_latex_specials(Title),
           Journal = Escape_latex_specials(Journal),
           DOI     = Escape_latex_specials(DOI),
           DOI = str_c("\\textcolor{blue}{", "http://dx.doi.org/", DOI, "}",  sep = "")) # Link to the article
```
  
```{r GS}

  My_GS <- scholar::get_profile("NF5SYm8AAAAJ&hl")

```

\vspace{-0.1cm}
\footnotesize 
\rightline{\textcolor{darktext}{"Expert on environmental research, statistics, spatial data analysis, and modelling."}} 
\normalsize

# Education
\vspace{-0.20cm}
```{r Education,  results = 'asis'}

 edu_ORCID <- orcid_educations(id)
  
  df_edu <- dplyr::bind_rows(edu_ORCID[[id]]$`affiliation-group`$summaries) %>% 
    select(`education-summary.start-date.year.value`,
           `education-summary.end-date.year.value`,
           `education-summary.role-title`,
           `education-summary.organization.name`,
           `education-summary.organization.address.city`,
           `education-summary.organization.address.country`) %>% 
    rename(Year_Start = `education-summary.start-date.year.value`,
           Year_End   = `education-summary.end-date.year.value`,
           Title      = `education-summary.role-title`,
           Uni        = `education-summary.organization.name`,
           City       = `education-summary.organization.address.city`,
           Country    = `education-summary.organization.address.country`) 
  
  df_edu %>% 
    mutate(Year_End = str_sub(Year_End, -2), 
           Title = bold_text(Title)) %>%
    unite(Year, Year_Start, Year_End, sep = "-", na.rm = TRUE) %>% 
    unite(Details, Title, Uni, City, Country, sep = ", ", na.rm = TRUE) %>% 
    CV_table()
  
```

\vspace{-0.75cm}
# Experience
\vspace{-0.20cm}
```{r experience, results = 'asis'}
  
  exp_ORCID <- orcid_employments(id)
  
  df_exp <- dplyr::bind_rows(exp_ORCID[[id]]$`affiliation-group`$summaries) %>% 
    select(`employment-summary.start-date.year.value`,
           `employment-summary.end-date.year.value`,
           `employment-summary.role-title`,
           `employment-summary.organization.name`,
           `employment-summary.department-name`,
           `employment-summary.organization.address.city`,
           `employment-summary.organization.address.country`) %>% 
    rename(Year_Start = `employment-summary.start-date.year.value`,
           Year_End   = `employment-summary.end-date.year.value`,
           Role       = `employment-summary.role-title`,
           Company    = `employment-summary.organization.name`,
           Depart     = `employment-summary.department-name`,
           City       = `employment-summary.organization.address.city`,
           Country    = `employment-summary.organization.address.country`) 
  
  df_exp %>% 
    mutate(Year_End = str_sub(Year_End, -2), 
           Role = bold_text(Role)) %>%
    unite(Year, Year_Start, Year_End, sep = "-", na.rm = TRUE) %>% 
    unite(Details, Role, Company, Depart, City, Country, sep = ", ", na.rm = TRUE) %>% 
    CV_table()
  
```
\vspace{-0.7cm}
# Professional Services
\vspace{-0.20cm}
```{r Services, results = 'asis'} 

  tribble(
    ~Year, ~Institution, ~Role,
    "2018-19", "\\textbf{International Atomic Energy Agency (IAEA)}", "Expert missions on Radon Mapping and National Radon Action Plans: Peru (August 2018), Cyprus (October 2018), Lithuania (July 2019)",
    
    "2018", "\\textbf{European Commission, Joint Research Centre (JRC)}", "Invite as an expert to the meeting -Working Group Meeting on Indoor Radon Dose- (May 2018, Ispra, Italy)"
  ) %>% 
    mutate(Details = str_c(Institution, Role, sep = ", ")) %>%
    select(Year, Details) %>%
    CV_table()

```

\vspace{-0.7cm}
# Professional memberships
\vspace{-0.20cm}
```{r memberships, results = 'asis'}
   
  mem_ORCID <- orcid_memberships(id)
  
  df_mem <- dplyr::bind_rows(mem_ORCID[[id]]$`affiliation-group`$summaries) %>% 
    select(`membership-summary.start-date.year.value`,
           `membership-summary.end-date`,
           `membership-summary.role-title`,
           `membership-summary.organization.name`,
           `membership-summary.department-name`,
           `membership-summary.organization.address.city`,
           `membership-summary.organization.address.country`) %>% 
    rename(Year_Start = `membership-summary.start-date.year.value`,
           Year_End   = `membership-summary.end-date`,
           Role       = `membership-summary.role-title`,
           Company    = `membership-summary.organization.name`,
           Depart     = `membership-summary.department-name`,
           City       = `membership-summary.organization.address.city`,
           Country    = `membership-summary.organization.address.country`) 

  df_mem %>% 
    mutate(Company = bold_text(Company)) %>%
    unite(Year, Year_Start, Year_End, sep = "-", na.rm = TRUE) %>% 
    unite(Details, Company, Depart, City, Country, sep = ", ", na.rm = TRUE) %>% 
    CV_table()
  
```
\vspace{-0.7cm}
# Honours and Awards
\vspace{-0.20cm}
```{r funding, results = 'asis'}

  fund_ORCID <- orcid_fundings(id)
  
  df_fund <- dplyr::bind_rows(fund_ORCID[[id]][[2]]$`funding-summary`) %>% 
    select(type,
           `start-date.year.value`,
           `end-date.year.value`,
           title.title.value,
           organization.name,
           organization.address.city,
           organization.address.country) %>% 
    rename(Type = type,
           Year_Start = `start-date.year.value`,
           Year_End = `end-date.year.value`,
           Title = title.title.value,
           Company = organization.name,
           City = organization.address.city, 
           Country = organization.address.country)
  
```

```{r awards, results = 'asis'}

  df_fund %>% 
    filter(Type == "award") %>%
    mutate(Title = bold_text(Title)) %>%
    rename(Year = Year_Start) %>%
    unite(Details, Title, Company, City, Country, sep = ", ", na.rm = TRUE) %>% 
    CV_table()

```
\vspace{-0.75cm}
# Other skills
\vspace{-0.15cm}
+ Advanced R experience and Geographic Information System (R and ArcGIS) 
+ Language skills: Spanish (mother tongue); English (fluent); Norwegian (basic)
