---
name: Javier 
surname: Elío
date: "`r format(Sys.time(), '%B, %Y')`"
position: Researcher | Environemntal sciences | Data Sciences
address: Haugesund (Norway)
phone: +47 4125 91 17
email: javiereliomedina@gmail.com
website: https://javierelio.netlify.com/
github: javiereliomedina
linkedin: javiereliomedina
twitter: Elio_Javi
output: vitae::awesomecv
header-includes:
  - \usepackage{colortbl}
  - \usepackage{longtable}
  - \usepackage{float}
  - \arrayrulecolor{white}
  - \definecolor{darktext}{HTML}{414141}
  - \definecolor{blue}{rgb}{0.0, 0.0, 1.0}
  
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
library(tidyverse)
library(purrr)
library(knitr)
library(kableExtra)
library(rorcid)
library(rcrossref)
  
source("CV_table.R")
source("Escape_latex_specials.R")
```

```{r ORCID_Works}
# Get ORCID API Key and save it in Renviron  
# orcid_auth()               # API key (without Bearer)
# usethis::edit_r_environ()  # Open up the Renviron file
# save the key as: ORCID_TOKEN="yourkey"
# Restart the R session
# We can see the key with Sys.getenv("ORCID_TOKEN")

# When possible I choose "Scopus - Elsevier" as the "Preferred Source" and delate the rest
# that way all articles will have the same format

# Get works
  id <- "0000-0003-0624-2345"
  out <- works(orcid_id(id)) 
  wks <- orcid_works(id, out$`put-code`)

# Alternative names and bold my surname in the pdf
  replace_my_name <- function(x) {
    x <- str_replace_all(x, "Elio", "Elío")
    x <- str_replace_all(x, "de Elío", "Elío")
    x <- str_replace_all(x, "Medina, J.E.", "Elío, J.")
    x <- str_replace_all(x, "Elío", "\\\\textbf{Elío}")
    }

# Bold text in the pdf
  bold_text <- function(x) {x <- str_c("\\textbf{", x, "}")}

# Extract publication information 
  pubs <- wks[[id]] %>% 
    pluck("works") %>% 
    bind_rows() %>% 
    as_tibble() %>% 
    unnest(`work.external-ids.external-id`) %>% 
    group_by(`work.put-code`) %>% 
    summarize(Pub_type = work.type,
              Pub_year = `work.publication-date.year.value`,
              Pub_authors = `work.contributors.contributor`,
              Pub_title = work.title.title.value,
              Pub_journal = `work.journal-title.value`,
              Pub_DOI = `external-id-value`) %>% 
    ungroup() %>% 
    distinct(Pub_title, .keep_all = TRUE) %>%
    # Get authors
    unnest(Pub_authors) %>% 
    group_by(Pub_title) %>% 
    mutate(Pub_authors = paste(`credit-name.value`, collapse = ", ")) %>% 
    ungroup() %>% 
    select(starts_with("Pub")) %>% 
    distinct(Pub_title, .keep_all = TRUE) %>% 
    # Correct some DOIs and my surname
    mutate(Pub_DOI = replace(Pub_DOI, Pub_DOI == "2-s2.0-84899952872", "10.30955/gnj.001242"), 
           Pub_DOI = replace(Pub_DOI, Pub_DOI == "2-s2.0-84899963838", "10.30955/gnj.001241"),
           Pub_authors = replace_my_name(Pub_authors)) %>%
    # Only articles and books chapters
    filter(Pub_type == "journal-article" | Pub_type == "book")      
  
# Add volume and pages 
  VP <- rcrossref::cr_cn(dois = pubs$Pub_DOI, format = "bibtex")
  
  pubs <- pubs %>%
    mutate(Pub_volume = str_match(VP, "volume = \\{(.*[0-9])")[,2],
           Pub_pages = str_match(VP, "pages = \\{(.*[0-9])")[,2]) 
# Remove latex symbols for knit
  pubs <- pubs %>%
    mutate(Pub_authors = Escape_latex_specials(Pub_authors),
           Pub_title   = Escape_latex_specials(Pub_title),
           Pub_journal = Escape_latex_specials(Pub_journal),
           Pub_DOI     = Escape_latex_specials(Pub_DOI),
           Pub_DOI = str_c("\\textcolor{blue}{", "http://dx.doi.org/", Pub_DOI, "}",  sep = "")) # Link to the article
```
  
```{r GS}

  My_GS <- scholar::get_profile("NF5SYm8AAAAJ&hl")

```

\vspace{-0.1cm}
\footnotesize 
\rightline{\textcolor{darktext}{"Expert on environmental research, statistics, spatial data analysis, and modelling."}} 
\normalsize

\vspace{0.5cm}
# Career Summary
\vspace{-0.1cm}
I am an Engineer from the Technical University of Madrid (Spain) with 10+ years of research experience. I have done an MSc in Environmental Research, Modelling and Risk Assessment, and a PhD in Geosciences. My degrees, and posterior professional development, have qualified me in a wide range of topics. I have experience, for example, in monitoring geological storage of $CO_2$, in geochemical characterization of contaminated sites, and in developing new methods for measuring microplastics. Furthermore, I have applied advanced modelling to evaluate the influence of geology on indoor radon levels. Recently I have started a postdoc in Geoinformatics on Migration Modelling at Aalborg University (Denmark). I am collaborating with the research group of Applied Marine Microbiology at Høgskulen på Vestlandet (Norway), where I have presented several projects for funding to the Norwegian Research Council, NordForsk, and the European Commission (Marie Sklodowska-Curie).

My research interests are: 

+	Environmental risk assessment
+ Statistics, spatial data analysis, and geostatistics
+ Geographic information systems
+ R language

# Education
\vspace{-0.1cm}
```{r Education,  results = 'asis'}

  orcid_educations(id)[[id]] %>%
    pluck("affiliation-group", "summaries") %>% 
    bind_rows() %>% 
    select("education-summary.start-date.year.value",
           "education-summary.end-date.year.value",
           "education-summary.role-title",
           "education-summary.organization.name",
           "education-summary.organization.address.city",
           "education-summary.organization.address.country") %>% 
    rename(Year_Start = "education-summary.start-date.year.value",
           Year_End   = "education-summary.end-date.year.value",
           Title      = "education-summary.role-title",
           Uni        = "education-summary.organization.name",
           City       = "education-summary.organization.address.city",
           Country    = "education-summary.organization.address.country") %>% 
    mutate(Year_End = str_sub(Year_End, -2), 
           Title = bold_text(Title)) %>%
    unite(Year, Year_Start, Year_End, sep = "-", na.rm = TRUE) %>% 
    unite(Details, Title, Uni, City, Country, sep = ", ", na.rm = TRUE) %>%
    select(Year, Details) %>%
    arrange(desc(Year)) %>% 
    CV_table()
  
```

\vspace{-0.5cm}
# Experience
\vspace{-0.1cm}
```{r experience, results = 'asis'}

  orcid_employments(id)[[id]] %>%
    pluck("affiliation-group", "summaries") %>% 
    bind_rows() %>% 
    select("employment-summary.start-date.year.value",
           "employment-summary.end-date.year.value",
           "employment-summary.role-title",
           "employment-summary.organization.name",
           "employment-summary.department-name",
           "employment-summary.organization.address.city",
           "employment-summary.organization.address.country") %>% 
    rename(Year_Start = "employment-summary.start-date.year.value",
           Year_End   = "employment-summary.end-date.year.value",
           Role       = "employment-summary.role-title",
           Company    = "employment-summary.organization.name",
           Depart     = "employment-summary.department-name",
           City       = "employment-summary.organization.address.city",
           Country    = "employment-summary.organization.address.country") %>% 
    mutate(Year_End = str_sub(Year_End, -2), 
           Role = bold_text(Role)) %>%
    unite(Year, Year_Start, Year_End, sep = "-", na.rm = TRUE) %>% 
    unite(Details, Role, Company, Depart, City, Country, sep = ", ", na.rm = TRUE) %>% 
    select(Year, Details) %>%
    arrange(desc(Year)) %>% 
    CV_table()
  
```

\vspace{-0.5cm}
# Invited Positions
\vspace{-0.1cm}
```{r inv_positions, results = 'asis'} 

  orcid_invited_positions(id)[[id]] %>%
    pluck("affiliation-group", "summaries") %>% 
    bind_rows() %>% 
    select("invited-position-summary.start-date.year.value",
           "invited-position-summary.end-date.year.value",
           "invited-position-summary.role-title",
           "invited-position-summary.organization.name",
           "invited-position-summary.department-name",
           "invited-position-summary.organization.address.city",
           "invited-position-summary.organization.address.country") %>% 
    rename(Year_Start = "invited-position-summary.start-date.year.value",
           Year_End   = "invited-position-summary.end-date.year.value",
           Role       = "invited-position-summary.role-title",
           Company    = "invited-position-summary.organization.name",
           Depart     = "invited-position-summary.department-name",
           City       = "invited-position-summary.organization.address.city",
           Country    = "invited-position-summary.organization.address.country") %>% 
    mutate(Year_End = str_sub(Year_End, -2), 
           Role = bold_text(Role)) %>%
    unite(Year, Year_Start, Year_End, sep = "-", na.rm = TRUE) %>% 
    unite(Details, Role, Company, Depart, City, Country, sep = ", ", na.rm = TRUE) %>% 
    select(Year, Details) %>%
    arrange(desc(Year)) %>% 
    CV_table()
  
```

\vspace{-0.5cm}
# Professional memberships
\vspace{-0.1cm}
```{r memberships, results = 'asis'}

  orcid_memberships(id)[[id]] %>%
    pluck("affiliation-group", "summaries") %>% 
    bind_rows() %>% 
    select("membership-summary.start-date.year.value",
           "membership-summary.end-date",
           "membership-summary.role-title",
           "membership-summary.organization.name",
           "membership-summary.department-name",
           "membership-summary.organization.address.city",
           "membership-summary.organization.address.country") %>% 
    rename(Year_Start = "membership-summary.start-date.year.value",
           Year_End   = "membership-summary.end-date",
           Role       = "membership-summary.role-title",
           Company    = "membership-summary.organization.name",
           Depart     = "membership-summary.department-name",
           City       = "membership-summary.organization.address.city",
           Country    = "membership-summary.organization.address.country") %>% 
    mutate(Company = bold_text(Company)) %>%
    unite(Year, Year_Start, Year_End, sep = "-", na.rm = TRUE) %>% 
    unite(Details, Company, Depart, City, Country, sep = ", ", na.rm = TRUE) %>%
    select(Year, Details) %>%
    arrange(desc(Year)) %>% 
    CV_table() 
  
```

\vspace{-0.5cm}
# Professional Services
\vspace{-0.1cm}
```{r Services, results = 'asis'} 

  orcid_services(id)[[id]] %>%
    pluck("affiliation-group", "summaries") %>% 
    bind_rows() %>% 
    select("service-summary.start-date.year.value",
           "service-summary.end-date.year.value",
           "service-summary.role-title",
           "service-summary.organization.name",
           "service-summary.department-name",
           "service-summary.organization.address.city",
           "service-summary.organization.address.country") %>% 
    rename(Year_Start = "service-summary.start-date.year.value",
           Year_End   = "service-summary.end-date.year.value",
           Role       = "service-summary.role-title",
           Company    = "service-summary.organization.name",
           Depart     = "service-summary.department-name",
           City       = "service-summary.organization.address.city",
           Country    = "service-summary.organization.address.country") %>% 
    mutate(Year_End = str_sub(Year_End, -2), 
           Company = bold_text(Company)) %>%
    unite(Year, Year_Start, Year_End, sep = "-", na.rm = TRUE) %>% 
    unite(Details, Company, Depart, City, Country, sep = ", ", na.rm = TRUE) %>% 
    select(Year, Details) %>%
    arrange(desc(Year)) %>% 
    CV_table()
  
```

\vspace{-0.5cm}
# Funding projects
\vspace{-0.1cm}
```{r funding, results = 'asis'}
  
  df_fund <- orcid_fundings(id)[[id]] %>%
    pluck("group", "funding-summary") %>% 
    bind_rows() %>% 
    select(type,
           "start-date.year.value",
           "end-date.year.value",
           title.title.value,
           organization.name,
           organization.address.city,
           organization.address.country) %>% 
    rename(Type = type,
           Year_Start = "start-date.year.value",
           Year_End = "end-date.year.value",
           Title = title.title.value,
           Company = organization.name,
           City = organization.address.city, 
           Country = organization.address.country)

```

```{r Projects, results = 'asis'}

  df_fund %>% 
    filter(Type == "grant") %>%
    mutate(Year_End = str_sub(Year_End, -2), 
           Title = bold_text(Title)) %>%
    unite(Year, Year_Start, Year_End, sep = "-", na.rm = TRUE) %>%
    unite(Details, Title, Company, City, Country, sep = ", ", na.rm = TRUE) %>%
    select(Year, Details) %>%
    arrange(desc(Year)) %>% 
    CV_table()

``` 
\vspace{-0.5cm}

# Honours and Awards
\vspace{-0.1cm}
```{r awards, results = 'asis'}
  
  df_fund %>% 
    filter(Type == "award") %>%
    mutate(Title = bold_text(Title)) %>%
    rename(Year = Year_Start) %>%
    unite(Details, Title, Company, City, Country, sep = ", ", na.rm = TRUE) %>% 
    select(Year, Details) %>%
    arrange(desc(Year)) %>% 
    CV_table()

```
\vspace{-0.5cm}
# Teaching Experience
\vspace{-0.1cm}
```{r teaching, results = 'asis'}

teching <- tribble(~Year, ~Role, ~City, ~Country, ~Description, ~Uni, ~Type,
2017,	"External PhD examiner",	"Madrid", "ES",	"Thesis: “Integration of remote sensing and statistical techniques for detecting CO2 leaks in geological storage areas through the study of natural analogues, Miguel A. Rincones Salinas", "Technical University of Madrid",	"PhD Examiner",

2017,	"Co-supervisor of a Master thesis in Environmental Sciences",	"Dublin", "IE",	"Assessing the contribution of Quaternary deposits to the soil radon budget in Ireland", "Trinity College Dublin, School of Natural Sciences, Geology", "Supervision",

2017,	"Co-supervisor of an Earth Science Dissertation",	"Dublin", "IE", "Evaluating two techniques of soil gas radon detection in application, performance and against indoor radon concentrations", "Trinity College Dublin, School of Natural Sciences, Geology", "Supervision",

2016,	"Co-supervisor of a Master thesis in Environmental Sciences",	"Dublin", "IE", "Linking radon concentrations between the natural and built environments", "Trinity College Dublin, School of Natural Sciences, Geology", "Supervision",

2018,	"Teaching assistant",	"Dublin", "IE",	"10 day geological residential field-school in SE Spain", "Trinity College Dublin, School of Natural Sciences, Geology", "Lectures",

2017,	"GIS module in MSc Environmental Science", "Dublin", "IE",	"Lecture: A new indoor radon risk map of Ireland. Geology, School of Natural Sciences", "Trinity College Dublin, School of Natural Sciences, Geology", "Lectures",

2016,	"Michaelmas Semester 2016 - Geology Seminar Series", "Dublin", "IE",	"Modelling Indoor Radon Concentration: Towards a High-Resolution Indoor Radon Map of Ireland",  "Trinity College Dublin, School of Natural Sciences, Geology", "Lectures",

2016,	"Teaching assistant",	"Dublin", "IE",	"10 day geological residential field-school in SE Spain", "Trinity College Dublin, School of Natural Sciences, Geology", "Lectures",

2013,	"Summer school in Carbon Capture and Storage",	"Ponferrada", "ES", "Surface and subsurface monitoring of a CO2 storage site: theory and practice", "University of León", "Lectures"
)
```
 
## PhD Examiner
\vspace{-0.1cm}
```{r PhD Examiner, results = 'asis'}

  teching %>% 
    filter(Type == "PhD Examiner") %>%
    mutate(Role = bold_text(Role)) %>%
    unite(Details, Role, Description, Uni, City, Country, sep = ", ") %>% 
    select(Year, Details) %>%
    arrange(desc(Year)) %>% 
    knitr::kable(col.names = NULL, escape = FALSE, align = 1L, booktabs = TRUE) %>%
    kableExtra::kable_styling(full_width = F) %>%
    kableExtra::column_spec(1, color = "darktext", width = "3.5em") %>%
    kableExtra::column_spec(2, color = "darktext", width = "40.5em")
  
``` 

\vspace{-0.5cm}
## Supervision
\vspace{-0.1cm}
```{r Supervision, results = 'asis'}

  teching %>% 
    filter(Type == "Supervision") %>%
    mutate(Role = bold_text(Role)) %>%
    unite(Details, Role, Description, Uni, City, Country, sep = ", ") %>% 
    select(Year, Details) %>%
    arrange(desc(Year)) %>% 
    CV_table()

```

\vspace{-0.5cm}
## Lectures/Seminars
\vspace{-0.1cm}
```{r Lectures, results = 'asis'}

  teching %>% 
    filter(Type == "Lectures") %>%
    mutate(Role = bold_text(Role)) %>%
    unite(Details, Role, Description, Uni, City, Country, sep = ", ") %>% 
    select(Year, Details) %>%
    arrange(desc(Year)) %>% 
    CV_table()
  
```

\vspace{-0.5cm}
# Publications
\vspace{-0.1cm}
I have published **`r length(pubs$Pub_type)`** peer-reviewed journal articles, chapters or books on Environmental Science topics. I have also presented my research at 3 invited talks, and in several national and international conferences including AGU, EGU, EAGE, IGC and Goldschmidt. My metrics in **Google Scholar** are:

\vspace{8pt}
+ Total citations: `r My_GS$total_cites`
+ h-index: `r My_GS$h_index`
+ i10-index: `r My_GS$i10_index`
\vspace{8pt}

## Peer reviewed articles
\vspace{-0.1cm}
```{r Articles, results = 'asis'}

  pubs %>%
    filter(Pub_type == "journal-article") %>%
    unite(Pub_details, Pub_authors, Pub_title, Pub_journal, Pub_volume, Pub_pages, Pub_DOI, sep = ", ", na.rm = TRUE) %>% 
    select(Pub_year, Pub_details) %>%
    arrange(desc(Pub_year)) %>%
    CV_table()

```

\vspace{-0.5cm}
## Book chapters
\vspace{-0.1cm}
```{r books, results = 'asis'}

  A <- tibble(Pub_year = "2019",
              Pub_details = "European Commission, Joint Research Centre – Cinelli, G., De Cort, M., Tollefsen, T. (Eds.): European Atlas of Natural Radiation, Publication Office of the European Union, Luxembourg, 2019. ISBN 978-92-76-08259-0, Catalogue number KJ-02-19-425-EN-C, EUR 19425 EN. Printed by Bietlot in Belgium 2019 – 190 pp. – 30.1 cm— 42.4 cm, \\textcolor{blue}{http://dx.doi.org/10.2760/520053}.") # Add document manually 
  
  B <- pubs %>%
    filter(Pub_type == "book") %>%
    unite(Pub_details, Pub_authors, Pub_title, Pub_journal, Pub_volume, Pub_pages, Pub_DOI, sep = ", ", na.rm = TRUE) %>% 
    select(Pub_year, Pub_details) %>%
    arrange(desc(Pub_year)) 
  
  bind_rows(A, B) %>%
    CV_table()

```